---
title: "Ideology Correlations for Moral/Emotional Contagion -- (w/o Topical Phrases)"
author: "Julian Wills and Billy Brady"
date: "November 5th, 2015"
output: pdf_document
---


```{r, echo=F, results='hide', include=F}

###TO DO:
#- rerun analyses w/o username=20998647 (@weatherchannel) for NM_NE cell
#- rename diffID back to sdID in dRT10 data


# load packages  --------------------------------------------------------
require(magrittr) || {install.packages("magrittr"); require(magrittr)}
require(dplyr) || {install.packages("dplyr"); require(dplyr)}
require(reshape2) || {install.packages("reshape2"); require(reshape2)}
require(ggplot2) || {install.packages("ggplot2"); require(ggplot2)}
source("C:/Users/Julian/GDrive/PGGfMRI/Behav/Scripts/helpFunc.r")


if (grepl("^C:/",getwd())) {
  userDir <- "C:/Users/Julian/GDrive" #PC
} else {
  userDir <- "/Users/julian/GDrive" #Mac
}

setwd(paste0(userDir,"/1 Twitter Project/pythonScripts/ClimateChange/Combined/noTopic"))
dAll <- tbl_df(read.csv("joinedRTs.csv",header=T)) %>% rename(tid=tID,rtid=rtID)

setwd(paste0(userDir,"/1 Twitter Project/pythonScripts/ClimateChange/Combined/noTopic"))
dCjoin <- tbl_df(read.csv("joinedRTs.csv",header=T,sep=",")) %>% mutate(diffID=sqrt(abs(tID-rtID)),ex.tID=abs(tID),ex.rtID=abs(rtID)) %>% 
  filter(!author==20998647)

dCjoin2 <- dCjoin %>% group_by(cond,author) %>% 
  summarise(varID=sd(rtID),tID=mean(tID),rtID=mean(rtID),ex.tID=mean(ex.tID),ex.rtID=mean(ex.rtID),
            M=mean(M),E=mean(E),count=n(),diffID=mean(abs(tID-rtID))) %>% 
  mutate(diffID=abs(tID-rtID),count.Tr=log(log(count+1)+1),
         meanID=(tID+rtID)/2,count.Tr2=count/sum(count),varID.Tr=sqrt(varID),
         diffID.Tr=sqrt(diffID)) %>% arrange(desc(count))

load("climateRT10_dvs.RData") #top retweet data

dCRT10 %<>% mutate(diffID.Tr=sqrt(diffID))

```


#Variable Guide:
###tID = ideology of original tweet author (negative = liberal; 0 = centrist; postive = conservative)
###rtID = ideology of retweeter (in most cases, averaged per tweet)
###ex.tID = ideological extremity (i.e. absolute value) of author (0 = centrist)
###ex.rtID = ideological extremity (i.e. absolute value) of retweeter 
###diffID = ideological difference (absolute value) between author and (avg.) retweeter (0 = no difference)
###M = moral (1); nonmoral (-1)
###E = emotional (1); unemotional (-1)
###cond = Four Conditions: M_E, M_NE, NM_E, NM_NE

***

#Correlations, Linear Models, and Unpacking Interactions

***

## What's the relation between ideological diversity and virality?
```{r}
dCjoin %<>% mutate(meanID=(tID+rtID)/2,
                   ideoSim=1/diffID)

dCjoin %>% group_by(cond) %>% summarise(Corr.T.RT=cor(tID,rtID)) %>% mutate_each(funs(round(.,2)),2)

ggplot(dCjoin,aes(x=tID,y=rtID,color=meanID)) + 
  geom_point(alpha=.1) +
  geom_smooth(method="lm",color="black") +
  scale_colour_gradient2(low="blue", mid="grey",high="red",limits=c(-2,2)) +
  theme(panel.background = element_rect(fill = "white")) +
  xlab("Ideology of Tweet Author") + ylab("Ideology of Retweeter") +
  facet_wrap("cond",nrow = 2)

ggplot(dCjoin,aes(x=tID,y=rtID,color=meanID)) + 
  geom_point(alpha=.5,aes(size=diffID)) +
  geom_smooth(method="lm",color="black") +
  scale_colour_gradient2(low="blue", mid="grey",high="red",limits=c(-2,2)) +
  theme(panel.background = element_rect(fill = "white")) +
  xlab("Ideology of Tweet Author") + ylab("Ideology of Retweeter") +
  facet_wrap("cond",nrow = 2)

ggplot(dCRT10,aes(x=tID,y=rtID,color=tID)) + 
  geom_point(alpha=1,aes(size=RTperDay.Tr)) +
  geom_smooth(method="loess",color="black") +
  scale_colour_gradient2(low="blue", mid="grey",high="red",limits=c(-2,2)) +
  theme(panel.background = element_rect(fill = "white")) +
  xlab("Ideology of Tweet Author") + ylab("Ideology of Retweeter") +
  facet_wrap("cond",nrow = 2)

ggplot(dCRT10,aes(x=tID,y=rtID,color=tID)) + 
  geom_point(alpha=1) +
  geom_smooth(method="loess",color="black") +
  scale_colour_gradient2(low="blue", mid="grey",high="red",limits=c(-2,2)) +
  theme(panel.background = element_rect(fill = "white")) +
  xlab("Ideology of Tweet Author") + ylab("Ideology of Retweeter") +
  facet_wrap("cond",nrow = 2)

ggplot(dCRT10,aes(x=tID,y=rtID,color=tID)) + 
  geom_point(alpha=1,aes(size=RTperDay.Tr)) +
  geom_smooth(method="loess",color="black") +
  scale_colour_gradient2(low="blue", mid="grey",high="red",limits=c(-2,2)) +
  theme(panel.background = element_rect(fill = "white")) +
  xlab("Ideology of Tweet Author") + ylab("Ideology of Retweeter") +
  facet_wrap("cond",nrow = 2)


ggplot(dCjoin2,aes(x=tID,y=rtID,color=meanID)) + 
  geom_point(alpha=1) +
  # geom_smooth(method="loess",color="black") +
  scale_colour_gradient2(low="blue", mid="grey",high="red",limits=c(-2,2)) +
  theme(panel.background = element_rect(fill = "white")) +
  xlab("Ideology of Tweet Author") + ylab("Ideology of Retweeter") +
  facet_wrap("cond",nrow = 2)

ggplot(dCjoin2,aes(x=tID,y=rtID,color=meanID)) + 
  geom_point(alpha=1,aes(size=count.Tr)) +
  geom_smooth(method="loess",color="black") +
  scale_colour_gradient2(low="blue", mid="grey",high="red",limits=c(-2,2)) +
  theme(panel.background = element_rect(fill = "white")) +
  xlab("Ideology of Tweet Author") + ylab("Ideology of (Average) Retweeter") +
  facet_wrap("cond",nrow = 2)

# ggplot(dCjoin2 %>% filter(varID.Tr>0),aes(x=tID,y=rtID,color=varID.Tr)) + 
#   geom_point(alpha=1,aes(size=count.Tr)) +
#   # geom_smooth(method="loess",color="black") +
#   scale_colour_gradient(low="grey",high="purple",limits=c(0,1.5)) +
#   theme(panel.background = element_rect(fill = "white")) +
#   xlab("Ideology of Tweet Author") + ylab("Ideology of (Average) Retweeter") +
#   facet_wrap("cond",nrow = 2)

# ggplot(dCjoin2,aes(x=tID,y=rtID,color=diffID)) + 
#   geom_point(alpha=1,aes(size=count.Tr2)) +
#   geom_smooth(method="loess",color="black") +
#   # scale_colour_gradient2(low="blue", mid="grey",high="red",limits=c(0,4)) +
#   theme(panel.background = element_rect(fill = "white")) +
#   xlab("Ideology of Tweet Author") + ylab("Ideology of (Average) Retweeter") +
#   facet_wrap("cond",nrow = 2)

```

***



## Output of Models
```{r}

# after adjusting for ideology of author, retweeters, and ideological extremity
lm(diffID ~ tID+rtID*M+rtID*E+M*E,data=dCjoin2) %>% summary() #main model

# morality plays a bigger role than emotion when it comes to ideological diversity
lm(diffID ~ tID+rtID+ex.tID*M+ex.tID*E,data=dCjoin2) %>% summary() #emo int w/ ex.tID
lm(diffID ~ tID+rtID+rtID*M+rtID*E,data=dCjoin2) %>% summary() #emo int w/ rtID
lm(diffID ~ tID+rtID+tID*M+tID*E,data=dCjoin2) %>% summary()

lm(diffID ~ ex.tID+ex.rtID*M+ex.rtID*E+M*E,data=dCjoin2) %>% summary() #huge morality interaction
lm(diffID ~ ex.tID*ex.rtID*M+ex.rtID*E+M*E,data=dCjoin2) %>% summary() #morality 3-way interaction
```

***


#Plots:


## In a moral context, emotional tweets accrue even narrower support
```{r}
# hist(dCjoin2$diffID.Tr)
# dCjoin2 %<>% mutate(diffID.Tr=sqrt(diffID))

ggplot(dCjoin2,aes(x=M,y=diffID.Tr,color=factor(E))) + 
  geom_smooth(method="lm")


dCjoin.S <- dCjoin2 %>% group_by(cond) %>% summarise(mean=mean(diffID.Tr),se=sd(diffID)/sqrt(n()))
ggplot(dCjoin.S,aes(x=cond,y=mean)) + 
  geom_errorbar(aes(ymin=mean-se, ymax=mean+se),
                width=.2,                    # Width of the error bars
                position=position_dodge(.9)) +
  xlab("Condition") +
  ylab("Ideological Variability")
```

# Morality narrows ideological clustering, especially when it's emotional

***

```{r}
# people are more likely to retweet authors of similar ideology
# emotion attenuates this relationship, but only if tweet is nonmoral
ggplot(dCjoin2,aes(x=diffID.Tr,y=count.Tr )) + 
  geom_smooth(method="lm",aes(color=cond)) +
  xlab("Ideological Difference between Author and Retweeters") +
  ylab("Number of Times Author gets Retweeted")

# dCRT10 %<>% mutate(diffID=abs(tID-rtID),diffID.Tr=sqrt(diffID))

#Viral tweets accrue wider ideological support
pairPlot(dCRT10 %>% select(RTperDay.Tr,count,RTperDay,diffID,diffID.Tr))

ggplot(dCRT10,aes(x=diffID.Tr,y=RTperDay.Tr )) + 
  geom_smooth(method="lm",aes(color=factor(cond))) +
  xlab("Ideological Difference between Author and Retweeters") +
  ylab("Number of Times Author gets Retweeted")

dCRT10 %>% group_by(cond) %>% 
  summarise(cor(tID,rtID),cor(diffID.Tr,RTperDay.Tr),cor(diffID.Tr,persistDays.Tr),cor(diffID.Tr,speedHrs.Tr))

# Viral tweets are less ideologically broad when moral. 
ggplot(dCRT10,aes(x=diffID.Tr,y=RTperDay.Tr )) + 
  geom_smooth(method="lm",aes(color=factor(M))) +
  # facet_wrap(factor("M")) +
  xlab("Ideological Difference between Tweet Author and Retweeters") +
  ylab("Number of Times Tweet gets Retweeted")

# Virality speed of tweets are less ideologically broad when moral. 
# Maybe small effect where emotion broadens ideologically diversity
ggplot(dCRT10,aes(x=diffID.Tr,y=speedHrs.Tr )) + 
  geom_smooth(method="lm",aes(color=factor(M))) +
  xlab("Ideological Difference between Tweet Author and Retweeters") +
  ylab("Speed of Virality (10 Retweets)")
ggplot(dCRT10,aes(x=diffID.Tr,y=speedHrs.Tr)) + 
  geom_smooth(method="lm",aes(color=factor(E))) +
  xlab("Ideological Difference between Tweet Author and Retweeters") +
  ylab("Speed of Virality (10 Retweets)")

# Ideologically similar tweets persist longer if they are emotional, but nonmoral (potential 3-way interaction)
ggplot(dCRT10,aes(x=diffID.Tr,y=persistDays.Tr)) + 
  geom_smooth(method="lm",aes(color=factor(E))) +
  facet_wrap("M") +
  xlab("Ideological Difference between Tweet Author and Retweeters") +
  ylab("Persistence of Tweets")

# Viral tweets tend to originate from nonextremists.
# Peristent tweets are sustained by extremists
pairPlot(dCRT10 %>% select(persistDays.Tr,persistDays,RTperDay,RTperDay.Tr,count,tID,rtID,ex.tID,ex.rtID))

# viral moral tweets are driven by centrists
ggplot(dCRT10,aes(x=ex.tID,y=RTperDay.Tr,color=factor(M))) + 
  geom_smooth(method="lm") +
  xlab("Ideological Extremity of Tweet Author") +
  ylab("Retweets per Day (Transformed)")

# In nonmoral context, emotionally viral tweets are driven by centrists, whereas nonemotional tweets are driven by extremists
ggplot(dCRT10,aes(x=ex.rtID,y=RTperDay.Tr,color=factor(cond))) + 
  geom_smooth(method="lm")

# Emotionally persistent tweets are driven by centrists, unless moral (then extremists)
ggplot(dCRT10,aes(x=ex.rtID,y=persistDays.Tr)) + 
  geom_smooth(method="lm",aes(color=factor(M))) +
  facet_wrap("E")

ggplot(dCjoin2,aes(x=rtID,y=diffID,color=factor(cond))) + 
  geom_smooth(method="loess")
ggplot(dCjoin2,aes(x=tID,y=rtID,color=factor(cond))) + 
  geom_point(alpha=.1) +
  geom_smooth(method="loess")
```

* People are more likely to retweet authors of similar ideology emotion attenuates this relationship, but only if tweet is nonmoral
* Viral tweets accrue wider ideological support
* Viral tweets are less ideologically broad when moral. 
* Virality speed of tweets are less ideologically broad when moral. Maybe small effect where emotion broadens ideologically diversity
* Ideologically similar tweets persist longer if they are emotional, but nonmoral (potential 3-way interaction)
* Viral tweets tend to originate from nonextremists.
* Peristent tweets are sustained by extremists
* viral moral tweets are driven by centrists
* In nonmoral context, emotionally viral tweets are driven by centrists, whereas nonemotional tweets are driven by extremists
* Emotionally persistent tweets are driven by centrists, unless moral (then extremists)

***

## Morality drives ideological clustering more than emotion (though emotion helps in nonmoral context)
```{r}
ggplot(dCjoin2,aes(x=tID,y=rtID,color=factor(E))) + 
  geom_point(alpha=.1) +
  geom_smooth(method="loess") +
  facet_grid(~M)

ggplot(dCjoin2,aes(x=tID,y=rtID,color=factor(E))) + 
  geom_point(alpha=.1) +
  geom_smooth(method="lm") +
  facet_grid(~M)
```

***

## Narrower clusters for moral tweets, especially for liberals when they are emotional
```{r}
ggplot(dCjoin2,aes(x=rtID,y=diffID,color=factor(E))) + 
  geom_point(alpha=.1) +
  geom_smooth(method="loess") +
  facet_grid(~M)
```

***

## On raw data, before clustering retweeters w/ original author. Vert/Horz lines reflect active users?
```{r}
ggplot(dCjoin,aes(x=tID,y=rtID,color=factor(E))) + 
  geom_point(alpha=.1) +
  geom_smooth(method="lm") +
  facet_grid(~M)

```

***

## In a moral context, emotional tweets accrue even narrower support
```{r}
ggplot(dCjoin2,aes(x=M,y=diffID,color=factor(E))) + 
  geom_smooth(method="lm")
```

***

## Political extremists retweet same ideology if tweet has moral content
```{r}
ggplot(dCjoin2,aes(x=ex.rtID,y=diffID,color=factor(M))) + 
  geom_point(alpha=.1) +
  geom_smooth(method="loess") 
ggplot(dCjoin2,aes(x=ex.rtID,y=diffID,color=factor(M))) + 
  geom_point(alpha=.1) +
  geom_smooth(method="lm")
```

***

## More extremism (author and retweeter) when content is moral 
```{r}
ggplot(dCjoin2,aes(x=ex.rtID,y=ex.tID,color=factor(M))) + 
  geom_smooth(method="loess") 
ggplot(dCjoin2,aes(x=ex.rtID,y=ex.tID,color=factor(M))) + 
  geom_smooth(method="lm")
```

***

## Ideologically Extreme Tweeters Accrue Narrower Support for Moral Tweets
```{r}
ggplot(dCjoin2,aes(x=ex.tID,y=diffID,color=factor(M))) + 
  geom_point(alpha=.1) +
  geom_smooth(method="loess") +
  xlab("Ideological Extremity of Original Tweet Author") +
  ylab("Ideological Distance of Retweeters") +
  ggtitle("Comparing Ideological Similarity of Author/Retweeters\n for Moral and Nonmoral Tweets (Loess Line)")

ggplot(dCjoin2,aes(x=ex.tID,y=diffID,color=factor(M))) + 
  geom_point(alpha=.1) +
  geom_smooth(method="lm") +
  xlab("Ideological Extremity of Original Tweet Author") +
  ylab("Ideological Distance of Retweeters") +
  ggtitle("Comparing Ideological Similarity of Author/Retweeters\n for Moral and Nonmoral Tweets (Linear Fit)")
```

***

#Code for heatmaps
```{r}
# # Heat maps ---------------------------------------------------------------
# 
# ## functions to construct heatmaps
# min <- -3.5
# max <- 3.5
# breaks <- 0.25
# 
# expand_data <- function(df, breaks=0.10, min=-4, max=4){
#   x <- df$rtid %>% as.numeric()
#   y <- df$tid %>% as.numeric()
#   x <- (round((x - min) / breaks, 0) * breaks) + min
#   y <- (round((y - min) / breaks, 0) * breaks) + min
#   tab <- table(x, y)
#   tab <- melt(tab)
#   tab$prop <- tab$value/sum(tab$value)
#   return(tab)
# }
# 
# ideoHeatMap <- function(df) { 
#   new.xy.me <- expand_data(df %>% filter(cond=="ME"),breaks=0.25) %>%  mutate(cond="ME")
#   new.xy.nme <- expand_data(df %>% filter(cond=="NME"),breaks=0.25) %>% mutate(cond="NME")
#   new.xy.mne <- expand_data(df %>% filter(cond=="MNE"),breaks=0.25) %>% mutate(cond="MNE")
#   new.xy.nmne <- expand_data(df %>% filter(cond=="NMNE"),breaks=0.25) %>%  mutate(cond="NMNE")
#   return (rbind(new.xy.me,new.xy.nme,new.xy.mne,new.xy.nmne))
# }
```



***
***
***



#Virality and Ideology

```{r}


if (grepl("^C:/",getwd())) {
  userDir <- "C:/Users/Julian/GDrive" #PC
} else {
  userDir <- "/Users/julian/GDrive" #Mac
}

setwd(paste0(userDir,"/1 Twitter Project/pythonScripts/allTweets"))

dCRT10 <- tbl_df(read.csv("climate/climateRetweetSpeed.csv",header=T,sep=",")) %>% 
  filter(!is.na(cond)) %>% 
  rename(tID=ID.0,rtID=meanID,diffID=sdID) %>% mutate(ex.tID=abs(tID),ex.rtID=abs(rtID)) %>% 
  mutate(M=ifelse(cond=="ME"|cond=="MNE",1,-1),E=ifelse(cond=="ME"|cond=="NME",1,-1)) %>% 
  mutate(diffID=sqrt(diffID),RTperDay.Tr=sqrt(log(RTperDay+1)),
         persistDays.Tr=log(log(persistDays+1)),
         speedHrs.Tr=log(1/speedHrs))


# hist(sqrt(dCRT10$diffID)) #sqrt transform to make more normal
hist(sqrt(log(dCRT10$RTperDay+1))) #sqrt + log + 1 --> more normal
hist(log(log(dCRT10$persistDays+1,10))) #sqrt + log + 1 --> more normal
hist(1/(log(dCRT10$speedHrs+1))^.15) #most normal

hist(log(1/dCRT10$speedHrs))


# morality plays a bigger role than emotion when it comes to ideological diversity
lm(diffID ~ tID+rtID+ex.tID+ex.rtID+M+E,data=dCRT10) %>% summary() #main effects
lm(diffID ~ tID+rtID+ex.tID+ex.rtID+M*E,data=dCRT10) %>% summary() #interactions


# which tweets predict retweets per day?
lm(RTperDay.Tr ~ tID+rtID+ex.tID+ex.rtID+M+E+diffID,data=dCRT10) %>% summary() #main effects

lm(persistDays ~ tID+rtID+ex.tID+ex.rtID+M+E,data=dCRT10) %>% summary() #emo int w/ ex.tID
lm(speedHrs ~ tID+rtID+ex.tID+ex.rtID+M+E,data=dCRT10) %>% summary() #emo int w/ ex.tID

lm(diffID ~ ex.tID+ex.rtID*M+ex.rtID*E+M*E,data=dCRT10) %>% summary() #Moral/Emo interaction
```

Model 1:
* Main effects: Morality/Emotion increase ideological clustering. 
* Checks: Tweets that accrue politically extreme support are less diverse. 

Model 2:
* Main effects: Now, only morality increases ideological clustering
* Interaction: this effect of morality is boosted when tweets are emotional


Retweets per Day:
Model 1: 
* Main effects: viral tweets associated with more liberal/extreme (re)tweeters. 
* Interaction: this effect of morality is boosted when tweets are emotional

#Plots:

```{r}
# pairPlot(dCRT10 %>% select(tID,rtID,ex.tID,ex.rtID,diffID,M,E,RTperDay.Tr,persistDays.Tr,speedHrs.Tr))

```
##Correlations/Scatterplots/LOESS
* Retweets/day associated w/ ideological diversity, conservative tweeters, nonmoral/nonemotional content (?),  and faster virality. 
* Persistent tweets associated w/ ideological clustering, politically extreme retweeters, and moral/emotional content 
* Speed of virality is associated w/ centrist (re)tweeters, ideological diversity, and nonmoral/nonemotional content(?)

***

```{r}
lm(RTperDay.Tr ~ tID+diffID+speedHrs.Tr+M+E,data=dCRT10) %>% summary() #main effects
lm(RTperDay.Tr ~ tID+diffID+speedHrs.Tr+M*E,data=dCRT10) %>% summary() #main effects

lm(RTperDay.Tr ~ tID+rtID+ex.tID+ex.rtID+M+E+diffID,data=dCRT10) %>% summary() #main effects
lm(RTperDay.Tr ~ tID+rtID+ex.tID+ex.rtID+M*E*diffID,data=dCRT10) %>% summary() #main effects

# speed
lm(speedHrs.Tr ~ ex.tID+ex.rtID+M+E+M*diffID,data=dCRT10) %>% summary() #main effects

# persistence
lm(persistDays.Tr ~ ex.rtID+M+E+diffID,data=dCRT10) %>% summary() #main effects
lm(persistDays.Tr ~ ex.rtID+M*E+diffID,data=dCRT10) %>% summary() #main effects


```
Virality:
* M1: virality associated w/ conservative tweeters, ideological clustering, and moral content. No interaction of moral/emotion. 
* M2: Interaction w/ diversity, moral/emotional

Speed:
* M1: virality speed is predicted by centrist tweeters and more political diversity. At first, main effect of morality -- but seems this is due to larger political diversity of nonmoral condition. 

Persistence:
* M1: main effects of morality and emotion seem to wash out the other associations w/ retweeter extremism and political diversity. 
* M2: Main effects persist, but no interaction. 

Conclusions: 
1. Virality and Speed are strongly associated w/ ideological diversity
2. Moral/Emotion interact with this relationship ^^ (still need to unpack)
3. Moral/emotional tweets persist longer

***

```{r}
ggplot(dCRT10,aes(x=diffID,y=RTperDay.Tr,color=cond)) + 
  geom_point(alpha=.6) +
  geom_smooth(method="lm")
  # facet_wrap("cond",nrow=2)

```

```{r}

ggplot(dCRT10,aes(x=tID,y=diffID,color=factor(cond))) + 
  geom_smooth(method="loess")
ggplot(dCRT10,aes(x=tID,y=diffID,color=factor(cond))) + 
  geom_smooth(method="lm")

ggplot(dCRT10,aes(x=M,y=diffID,color=factor(E))) + 
  geom_smooth(method="lm")

ggplot(dCRT10,aes(x=tID,y=diffID,color=factor(E))) + 
  geom_smooth(method="lm") +
  facet_grid(~M)

ggplot(dCRT10,aes(x=tID,y=rtID,color=factor(M))) + 
  geom_point(alpha=.6) +
  geom_smooth(method="lm")
```

* Main effects: Narrower ideological networks for moral and emotional content.
* Interaction? Emotional tweets increase liberal clustering when they're not moral, otherwise increases conservative clustering when it is moral. 

***

```{r}
ggplot(dCRT10,aes(x=diffID,y=RTperDay.Tr,color=factor(cond))) + 
  geom_smooth(method="lm")
ggplot(dCRT10,aes(x=tID,y=diffID,color=factor(cond))) + 
  geom_smooth(method="lm")

ggplot(dCRT10,aes(x=M,y=diffID,color=factor(E))) + 
  geom_smooth(method="lm")

ggplot(dCRT10,aes(x=tID,y=diffID,color=factor(E))) + 
  geom_smooth(method="lm") +
  facet_grid(~M)

ggplot(dCRT10,aes(x=tID,y=rtID,color=factor(M))) + 
  geom_point(alpha=.6) +
  geom_smooth(method="lm")
```

* Main effects: Narrower ideological networks for moral and emotional content.
* Interaction? Emotional tweets increase liberal clustering when they're not moral, otherwise increases conservative clustering when it is moral. 

***

#Ideology plots 

```{r, echo=FALSE}
# # create heatmap
# ggplot(ideoHeatMap(dAll %>% filter(topic=="G")), aes(x=y, y=x)) +
#   geom_tile(aes(fill=prop), colour="white") +
#   scale_fill_gradient(name="% of\ntweets", 
#                       low = "white", high = "black", 
#                       breaks=c(0, .0050, 0.010, 0.015, 0.02), limits=c(0, .021),
#                       labels=c("0.0%", "0.5%", "1.0%", "1.5%", ">2%")) +
#   labs(y="Estimated Ideology of Retweeter", x="Estimated Ideology of Author",
#        title="Ideological Correlations in Gun Tweets") + 
#   scale_y_continuous(expand=c(0,0), breaks=(-2:2), limits=c(-3, 3)) +
#   scale_x_continuous(expand=c(0,0), breaks=(-2:2), limits=c(-3, 3)) +
#   theme(panel.border=element_rect(fill=NA), panel.background = element_blank()) +
#   coord_equal()  +
#   facet_wrap(~ cond)
# 
# # create heatmap
# ggplot(ideoHeatMap(dAll %>% filter(topic=="M")), aes(x=y, y=x)) +
#   geom_tile(aes(fill=prop), colour="white") +
#   scale_fill_gradient(name="% of\ntweets", 
#                       low = "white", high = "black", 
#                       breaks=c(0, .0050, 0.010, 0.015, 0.02), limits=c(0, .021),
#                       labels=c("0.0%", "0.5%", "1.0%", "1.5%", ">2%")) +
#   labs(y="Estimated Ideology of Retweeter", x="Estimated Ideology of Author",
#        title="Ideological Correlations in Marriage Tweets") + 
#   scale_y_continuous(expand=c(0,0), breaks=(-2:2), limits=c(-3, 3)) +
#   scale_x_continuous(expand=c(0,0), breaks=(-2:2), limits=c(-3, 3)) +
#   theme(panel.border=element_rect(fill=NA), panel.background = element_blank()) +
#   coord_equal()  +
#   facet_wrap(~ cond)
# 
# # create heatmap
# ggplot(ideoHeatMap(dAll %>% filter(topic=="C")), aes(x=y, y=x)) +
#   geom_tile(aes(fill=prop), colour="white") +
#   scale_fill_gradient(name="% of\ntweets", 
#                       low = "white", high = "black", 
#                       breaks=c(0, .0050, 0.010, 0.015, 0.02), limits=c(0, .021),
#                       labels=c("0.0%", "0.5%", "1.0%", "1.5%", ">2%")) +
#   labs(y="Estimated Ideology of Retweeter", x="Estimated Ideology of Author",
#        title="Ideological Correlations in Climate Tweets") + 
#   scale_y_continuous(expand=c(0,0), breaks=(-2:2), limits=c(-3, 3)) +
#   scale_x_continuous(expand=c(0,0), breaks=(-2:2), limits=c(-3, 3)) +
#   theme(panel.border=element_rect(fill=NA), panel.background = element_blank()) +
#   coord_equal()  +
#   facet_wrap(~ cond)
# 
# dAll %>% filter(topic=="C") %>% group_by(cond) %>% summarise_each(funs(mean,sd),tid:rtid) %>% 
#   mutate_each(funs(round(.,2)),tid_mean:rtid_sd)
# 
# # Incomplete data ---------------------------------------------------------
# setwd("C:/Users/Julian/GDrive/1 Twitter Project/pythonScripts/")
# dGM <- tbl_df(read.csv(paste0(getwd(),"/","GayMarriage/gayMarriageMoral/","joinedRTs.csv"),header=T)) %>%      rename(tid=tID,rtid=rtID)
# dGC <- tbl_df(read.csv(paste0(getwd(),"/","GunControl/GC2013/","joinedRTs.csv"),header=T)) %>%                 rename(tid=tID,rtid=rtID)
# 
# 
# # create heatmap
# ggplot(ideoHeatMap(dGC %>% filter(M==1)), aes(x=y, y=x)) +
#   geom_tile(aes(fill=prop), colour="white") +
#   scale_fill_gradient(name="% of\ntweets", 
#                       low = "white", high = "black", 
#                       breaks=c(0, .0050, 0.010, 0.015, 0.02), limits=c(0, .021),
#                       labels=c("0.0%", "0.5%", "1.0%", "1.5%", ">2%")) +
#   labs(y="Estimated Ideology of Retweeter", x="Estimated Ideology of Author",
#        title="Ideological Correlations in Gun Control 2013 Tweets") + 
#   scale_y_continuous(expand=c(0,0), breaks=(-2:2), limits=c(-3, 3)) +
#   scale_x_continuous(expand=c(0,0), breaks=(-2:2), limits=c(-3, 3)) +
#   theme(panel.border=element_rect(fill=NA), panel.background = element_blank()) +
#   coord_equal()  +
#   facet_grid(. ~ cond)
# 
# dGC %>% group_by(cond) %>% filter(M==1) %>% summarise_each(funs(mean,sd),tid:rtid) %>% 
#   mutate_each(funs(round(.,2)),tid_mean:rtid_sd)
# 
# # create heatmap
# ggplot(ideoHeatMap(dGM %>% filter(M==1)), aes(x=y, y=x)) +
#   geom_tile(aes(fill=prop), colour="white") +
#   scale_fill_gradient(name="% of\ntweets", 
#                       low = "white", high = "black", 
#                       breaks=c(0, .0050, 0.010, 0.015, 0.02), limits=c(0, .021),
#                       labels=c("0.0%", "0.5%", "1.0%", "1.5%", ">2%")) +
#   labs(y="Estimated Ideology of Retweeter", x="Estimated Ideology of Author",
#        title="Ideological Correlations in Gay Marriage Tweets") + 
#   scale_y_continuous(expand=c(0,0), breaks=(-2:2), limits=c(-3, 3)) +
#   scale_x_continuous(expand=c(0,0), breaks=(-2:2), limits=c(-3, 3)) +
#   theme(panel.border=element_rect(fill=NA), panel.background = element_blank()) +
#   coord_equal()  +
#   facet_grid(. ~ cond)
# 
# dGM %>% group_by(cond) %>% filter(M==1) %>% summarise_each(funs(mean,sd),tid:rtid) %>% 
#   mutate_each(funs(round(.,2)),tid_mean:rtid_sd)
# 

# old code
# load in RT summary files
# setwd("C:/Users/Julian/GDrive/1 Twitter Project/pythonScripts/")
# dG <- tbl_df(read.csv(paste0(getwd(),"/","GunControl/Guns/split/filt/RT/","G_RT.csv"),header=T))
# dM <- tbl_df(read.csv(paste0(getwd(),"/","GayMarriage/marriage/split/RT/","M_RT.csv"),header=T))
# dC <- tbl_df(read.csv(paste0(getwd(),"/","ClimateChange/Combined/split/filt/append/RT/",
#                              "C_RT.csv"),header=T))
# dAll <- rbind(dG,dM,dC)
```

